%---------------------------%
%    nate-wilkins/resume    %
%---------------------------%

% --[ Notes ]-------------------------------------------------------------------\
% /
% - extra copies (3)
% - bring your business cards (5)
% - ask to take/have notes
%   - take notes on your copy
%   - something to write with
% - get there early (don't go in)
% - get business cards or write down names
% - make a list of references to hand out
% - make a list of questions to ask
% ------------------------------------------------------------------------------/

\documentclass[letterpaper,11pt]{article}
\author{nate-wilkins}
\date{\today}

\usepackage[empty]{fullpage}
\usepackage[pdftex]{hyperref}
\usepackage[usenames,dvipsnames]{color}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{verbatim}
\usepackage{marvosym}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx}

% --------------------------------------------------------------------[ DEBUG ]-\
%\usepackage{tikzpagenodes}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\lfoot{\thepage \hspace{1pt} of \pageref{LastPage}}

\usepackage[
  top    = .75cm,
  bottom = .75cm,
  left   =  1.25cm,
  right  =  1.25cm,
  marginparsep   = 0pt,
  marginparwidth = 0pt,
  % ----------------------------------------------------[ DEBUG :: Show Frame ]-\
  %showframe,
  ]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% -[ Custom Commands ]----------------------------------------------------------\
% /

% \rSkill*
\newcommand{\rSkillListStart}{\begin{itemize}[leftmargin=*,label={}]}
  \newcommand{\rSkillListEnd}{\end{itemize}\vspace{-5pt}}


% \rExp*
\newcommand{\rExpListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\rExp}[3]{
  \vspace{-.25em}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \large{\textbf{#1}} \textit{#2} & \textit{#3}
    \end{tabular*}\vspace{-.25em}
}
\newcommand{\rExpListEnd}{\end{itemize}}


% \rProj*
\newcommand{\rProjListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\rProj}[3]{
  \item\small{
    \textbf{[#1] #2}{: #3 \vspace{-2pt}}
  }
}
\newcommand{\rProjListEnd}{\end{itemize}\vspace{-5pt}}


% \rResp
\newcommand{\rRespListStart}{\begin{itemize}[label={-}]}
\newcommand{\rResp}[1]{
  \item\small{
    \textmd{#1 \vspace{0em}}
  }
}
\newcommand{\rRespListEnd}{\end{itemize}\vspace{.25em}}


% \rEdu*
\newcommand{\rEduListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\rEdu}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textit{\small#2} & \textit{#3} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\rEduListEnd}{\end{itemize}\vspace{-20pt}}

% \rOther*
\newcommand{\rOtherListStart}{\begin{itemize}[leftmargin=*,label={-}]}
\newcommand{\rOther}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} \textit{\small#2} & \textit{#3} \\
  \end{tabular*}\vspace{-5pt}}
\newcommand{\rOtherListEnd}{\end{itemize}\vspace{10pt}}

% \labelitemii
\renewcommand{\labelitemii}{$\circ$}


% -[ Document ]-----------------------------------------------------------------\
% /
\begin{document}

% -----------------------------------------------------[ DEBUG :: Guide Lines ]-\

% \begin{tikzpicture}[remember picture,overlay]
% \draw[red] (current page.north) -- (current page.south);
% \end{tikzpicture}

% -[ Header ]-------------------------------------------------------------------\
% /
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://code-null.com/about}{\Large Nathaniel Wilkins}} &
    \href{mailto:nate-wilkins@code-null.com}{nate-wilkins@code-null.com} \\
  \href{http://code-null.com/about}{code-null.com/about} & (585) 210-2403 \\
\end{tabular*}

% -[ Blurb ]--------------------------------------------------------------------\
% /
% TODO: ?

% -[ Sections ]-----------------------------------------------------------------\
% /
\section{Programming Skills}
\rSkillListStart
  \item{
    \textbf{Languages}{: Elixir, C\#, JavaScript, Python, SQL}
    \hfill
    \textbf{Technologies}{: GCP, Azure, React, Docker}
  }

  \item{
    \textbf{Development}{: S/W Design Patterns, OO Modeling and Design, SOLID
      Principles, Continuous Integration}
  }
\rSkillListEnd

\section{Experience}
\rExpListStart
  % ---------------[ Liazon ]---------------------------------------------------\
  \rExp  {Liazon} {Senior Software Engineer}                          {2015-2018}

  \rProjListStart
    % ----------[ BrightChoices ]-----------------------------------------------\
    \rProj {web} {BrightChoices} {Online private benefits exchange for large and
                                    small businesses worldwide.}

    \rRespListStart
      \rResp {Reduced department development costs by 26 hours a day by
                developing an easy-to-use, consistent, \\
                reproducible build pipeline written in \textbf{PowerShell}.}

      \rResp {Utilized \textbf{NServiceBus}, \textbf{MSMQ}, and messaging
                patterns to handle core business operations.}

      \rResp {Implemented \textbf{Windsor} facilities - logging, database
                transaction management, and event dispatching.}

      \rResp {Provided insights into \textbf{AngularJS} and front-end best
                practices.}

      \rResp {Refactored component services to use a \textbf{Windsor IoC}
                container to better manage component services \\
                and their dependencies.}

      \rResp {Implemented \textbf{SonarQube}, a code quality analysis tool,
                to help manage technical debt across the organization.}

      \rResp {Created \textbf{SpecFlow} integration tests to help put
                monolithic legacy code under test.}

      \rResp {Created \textbf{XUnit} component tests to solidify quoting,
                underwriting, and eligibility features.}

      \rResp {Collaborated with Operations to migrate our \textbf{TFS}
                repository of 18,000 files to \textbf{Git}.}
    \rRespListEnd

    % ----------[ Employee Search ]---------------------------------------------\
    \rProj {web} {Employee Search} {Internal presentation tool used by employers
                                      to manage employees on the BrightChoices
                                      platform.}
    \rRespListStart
      % TODO: Yeah?
      \rResp {Communicated closely with key stakeholders to develop a full
                functioning, self-contained application.}

      \rResp {Reduced BrightChoices legacy employee search result load times
                from 16s to 48ms.}

      \rResp {Developed core search functionality on top of
                \textbf{ElasticSearch} using \textbf{Mono C\#}.}

      \rResp {Utilized advanced \textbf{ElasticSearch} functionality including
                sharding, typeahead, and custom tokenizers.}

      \rResp {Implemented as a \textbf{Docker} container for portability and
                easier deployments to \textbf{Azure}.}

      \rResp {Developed custom sync tool with \textbf{Dapper} to align
                ``master'' employee records. Refactored later to \\
                implement Elastic's \textbf{LogStash}.}

      \rResp {Implemented a \textbf{RESTFful} API using \textbf{NancyFX} for
                data access.}

      \rResp {Developed \textbf{MSMQ} event hooks to keep employee records
                up-to-date with the BrightChoices platform.}

      \rResp {Developed front-facing \textbf{SPA} with \textbf{ReactJS} to
                organize employee information.}
    \rRespListEnd

    % ----------[ Insurance Inventory ]-----------------------------------------\
    \rProj {web} {Insurance Inventory} {Administration application
                                          used to manage insurance product
                                          configurations.}

    \rRespListStart
      \rResp {Communicated closely with key stakeholders to develop a full
                functioning application service.}

      \rResp {Provided leadership to a team of 6 to build and deploy the
                application service.}

      \rResp {Created \textbf{UML} diagrams and \textbf{\LaTeX} documents to
                facilitate communication between teams.}

      \rResp {Developed back-end functionality with \textbf{TopShelf} and
                \textbf{C\#}.}

      \rResp {Refactored existing BrightChoices front-end code written in
                \textbf{Razor} to talk to the new application service.}
    \rRespListEnd

    % -------------[ Ocelot Test Runner ]---------------------------------------\
    \rProj {native} {Ocelot Test Runner} {Developed an \textbf{Electron}
                                            application to run
                                            \textbf{SpecFlow} integration
                                            tests for QEs.}

    % -------------[ BrightChoices VR ]-----------------------------------------\
    \rProj {native} {BrightChoices VR} {``Online'' private benefits exchange for
                                          large and small businesses in virtual
                                          reality!}

    \rRespListStart
      \rResp {Developed a rudimentary shopping experience in
                \textbf{Virtual Reality} with \textbf{Unity} and the
                \textbf{HTC Vive}.}

      \rResp {Collaborated with two other team members to build a working
                prototype in a two-day hackathon.}
    \rRespListEnd
  \rProjListEnd

\pagebreak

  % ---------------[ Carestream Health ]----------------------------------------\
  \rExp  {Carestream Health} {Software Contractor}                    {2013-2015}
  \rProjListStart
    % -----------------[ NextGen Platform ]-------------------------------------\
    \rProj {web/native} {NextGen Platform} {Rewrite of the CaptureCommon
                                              Platform to architecture to
                                              support the next generation of
                                              X-Ray Solutions.}
    \rRespListStart
      \rResp {Served as a leading technical specialist.}

      \rResp {Developed \textbf{il18n} system with \textbf{angular-translate},
                \textbf{CLDR}, and \textbf{MomentJS}.}

      \rResp {Developed build and deployment infrastructure using \textbf{npm}
                and \textbf{NodeJS} integrated into \textbf{MSBuild}.}

      \rResp {Established \textbf{AngularJS} design patterns and best
                practices.}

      \rResp {Developed kVp, MA, and time components used in the X-Ray
                generator.}

      \rResp {Utilized \textbf{MassTransit} and \textbf{SignalR} to interface
                our web application directly with the modular XRS hardware.}

      \rResp {Developed an easy-to-use spinner control that could be applied to
                individual components.}

      \rResp {Collaborated with product teams to gather required functionality.}

      \rResp {Implemented modular configurations on build using \textbf{AngularJS}
                services for use by platform products.}
    \rRespListEnd

    % ----------[ Translations Manager ]----------------------------------------\
    \rProj {web} {Translations Manager} {Localization workflow application
                                           to manage the creation,
                                           maintenance, and processing of
                                           NextGen product translations.}

    \rRespListStart
      % TODO: Yeah?
      \rResp {Communicated closely with key stakeholders to develop a full
                functioning, self-contained application.}

      \rResp {Managed localizations for 25 languages and over 125,000
        translations with ease.}

      \rResp {Developed integrations into the \textbf{NextGen il18n}
                infrastructure. \\
              Created exporters for various formats
                (\textbf{XLIFF}, \textbf{XML}, \textbf{JSON}, and \textbf{CSV})}

      \rResp {Implemented a back-end \textbf{RESTful} API using
                \textbf{WebAPI2} to access languages, translations, products,
                and users.}

      \rResp {Implemented a front-end \textbf{SPA} using \textbf{AngularJS} and
                \textbf{ui-grid}.}

      \rResp {Implemented full-text search functionality using \textbf{SQL} and
                \textbf{NHibernate}.}

      \rResp {Developed entity based permissions system with \textbf{LINQ} and
                \textbf{ExpressionTrees} to limit user access to certain entities
                regarding their own state.}

      \rResp {Configured \textbf{IIS Web Deployments} to deploy to a local
                intranet. \\
              Later setup on \textbf{TravisCI} for automated deployments.}
    \rRespListEnd

    % -------------[ DRX Detector Applications ]--------------------------------\
    \rProj {native} {DRX Detector Applications} {Sample software to provide
                                                   partnered vendors to
                                                   create third party
                                                   applications to integrate
                                                   with the DRX Detector.}
    \rRespListStart
      \rResp {Utilized \textbf{.NET interop} to communicate with the
                \textbf{C/C++} DRX detector}

      \rResp {Developed a \textbf{C\#} API facade to encapsulate the
                DRX detector API.}

      \rResp {Removed over 10,000 unnecessary lines of code in the
                preexisting \textbf{WinForms} project.}
    \rRespListEnd

    % TODO: Mooooree
  \rProjListEnd
\rExpListEnd

\section{Projects}
\rProjListStart
  \rProj {web} {eslint-plugin-bdd} {Implemented an \textbf{ESLint} plugin to lint
                                      \textbf{BDD} specs.}

  \rProj {web} {code-null.com} {Developed a personal website using
                                  \textbf{Elixir} and hosted with
                                  \textbf{Google Firebase}.}

  \rProj {native} {EvE} {Developed reproducible development environments for
                            Windows and Ubuntu. Utilized \textbf{Docker} and
                            various software packages.}

  \rProj {native} {chocolatey-packages} {Implemented an \textbf{AU} repository
                                            to automatically create
                                            \textbf{Chocolatey} packages for
                                            software not packaged by their
                                            original maintainer.}
\rProjListEnd

\section{Education and Certifications}
\rEduListStart
  % ----------[ MCSD Programming in C\# ]---------------------------------------\
  \rEdu {MCSD Programming in C\#} {}                                       {2015}

  % ---------------[ Monroe Community College ]---------------------------------\
  \rEdu {Monroe Community College} {Rochester, NY}                    {2013-2014}

  \rRespListStart
    \rResp {Developed a configurable Jeopardy game with questions, sound, and
              even animations using Java.}

    \rResp {Developed a time scheduling web application to help users resolve
              conflicting schedules. Most notably tries to avoid Hamiltonian
              cycles of overlapping time. Pitched to office registrar for
              integration with the scheduling system.}
  \rRespListEnd
\rEduListEnd

\section{Other}
\rOtherListStart
  \rOther {Placed 2nd in the Synacor Hackathon.} {Buffalo, NY}             {2017}

  \rOther {Attended Abstractions.io conference.} {Pittsburgh, PA}          {2017}

  \rOther {Attended CodeMash conferences.} {Sandusky, OH}             {2016-2017}
\rOtherListEnd

\end{document}